\begin{itemize}
\item A main argument of \textit{Inference and Meaning} is that any language that makes essential use of non-logical, descriptive vocabulary must be understood as having that vocabulary standing in \ref{sellars_material_inference|materially good|} (rather than just logically good) inferences.
    \begin{itemize}
    \item A slogan for this: ``Concepts as involving laws (and inconceivable without them)''
        \begin{itemize}
        \item This is actually the title of an unintelligible essay by Sellars
        \item Luckily the title is the thesis, and that much is intelligible
        \end{itemize}
    \item Sellars claims logical vocabulary has the expressive job of making explicit the material proprieties of inference that articulate the content of non-logical concepts.
    \begin{itemize}
    \item More specifically than `logical', he means \emph{alethic modal} vocabulary: i.e. what's \emph{necessary} and what's \emph{possible}.
    \item Historical note: Frege is more explicit about this point than Sellars: that you can use this to distinguish logical vocabulary.
    \end{itemize}
    \item The \ref{montaigne_dog|Montaigne|example} example) highlights the difference between the capacity to use material inferences vs making that inference explicit:
        \begin{itemize}
        \item Dan Dennett argues that we have to take animals as grasping modus ponens because they treat some inferences as good and others as bad
        \item Sellars objects, saying that you \emph{could} make explicit the practical capacity the animal has via a statement of disjunctive syllogism
        \item But what is the surplus value of invoking that explicit expression? (Over simply describing what is the dog can do).
        \end{itemize}
    \item Talking about following rules very quickly gets into the \ref{regress_rules|regress of rules|}.
        \begin{itemize}
        \item There have to be some practical moves you're just allowed to make without them having to take the form of explicit premises (see \ref{tortoise|Tortoise and Achilles|Relevant to the regress of rules}).
        \item Sellars touches upon this in Reflections on Language Games.
            \begin{itemize}
            \item He talks about free/auxillary positions that you're always allowed to occupy.
            \item  We could have the auxillary position $\forall x, \psi(x)\vdash \phi(x)$ which would license us to move from a position $\psi(a)$ to a position $\phi(a)$, but we could also encode this with position for each possible move ($\psi(a)\vdash \phi(a)$, $\psi(b)\vdash\phi(b)$, ...).
            \item He ways that we could imagine replacing positions with moves, but it's not possible to imagine all moves being replaced with positions (`a game without moves is Hamlet without the Prince of Denmark').
            \end{itemize}
        \end{itemize}
    \end{itemize}
    \item Sellars is addressing tradition that wants some small set of explicit principles in accordance with which to reason. Any inference you think is good that isn't derivable from that small set of principles (e.g. modus ponens) is actually an infamy (has some suppressed premises). This is early analytic philosophy's embrace of the new logic. Sellar's contrary view (radical at the time) is that actually the reasoning could be completely in order, just with material proprieties of reasoning. You can still give/ask for reasons and mean that $p$, but what the logic does is give you meta-linguistic control to talk about what is a good inference and say that $p \vdash q$ is a good inference.\footnote{However, Sellars doesn't extrapolate from this that logic is an \emph{optional} superstructure in our lives - we need to be able to think and talk about the goodness of inferences.} \begin{itemize}
    \item Example: $A\vdash B$ where $A$ is ``she asked me to hand her the dish towel" and $B$ is ``I shall hand her the dish towel''. Traditional analytic philosophy will call this an infamy, since it does not explicitly state how her request engages my motivational structure. Sellars would want to say that this invocation of the desire makes explicit the endorsement of $A \vdash B$ rather than referring to some item of the world.

    \end{itemize}
    \item Brandom: logic is the organ of semantic self-consciousness. The set of concepts that lets us bring our endorsement of some inferences as good/bad (this endorsement as something that reasons can be given or asked for) into the game of giving/asking for reasons.
    \item Sellars complains about Carnap treating logical consequence as a syntactically definable relation between sentences. Just writing down the rules under a heading `rules' instead of `axioms' isn't making explicit the normative force they have (it leaves out the rulishness - that a rule is a rule for \emph{doing} something). This is a subtle point that doesn't matter for many purposes, but Sellars believes it's important if you want to understand what's going on with reasoning. Again, strong connection between this point and \emph{Achilles and the Tortoise}.
    \item ``There's an important difference between logical / modal / normative predicates on the one hand, and such predicates as `red' on the other.'' There's nothing to the formal except their role in reasoning, indeed, their role and make as meta linguistics sort of making explicit something about the ground level. For the latter, he wants to argue that these predicates too are meaningful insofar as their role in reasoning, but it's less obvious. \begin{itemize}
    \item ``Red is a quality''. This conveys the same information as the syntactical sentence ``\textit{Red} is a one place predicate.'' See \ref{modalities_norms|quote|reference}. What you're \emph{doing} in asserting that premise from which to reason (couched in modal vocabulary) is endorsing a principle in accordance with which to reason (couched in normative vocabulary).

    \item We cannot completely identify modal and normative statements with each other. Their relation is characterized by the \ref{say_convey|say/convey distinction|}.
    \end{itemize}
\end{itemize}








