Kant's \emph{normative} understanding of discursive practice\footnote{i.e. practice relating to \emph{concepts}}.

\begin{itemize}
    \item How do we understand the difference between sapient beings (e.g. people who think like us and use concepts) from mere responders to the natural environment? Here are two possible ways to think of it: \begin{itemize}
        \item $O$: An \emph{ontological} distintion: knowers are an actually different kind of thing (perhaps there is a presence of `mind stuff' or `spirit stuff').
        \item $D$: A \emph{deontological} distinction: we \emph{treat} knowers differently from objects. There are things that the agents are in a distinctive sense \emph{responsible} for \footnote{This point is shared by the later Wittgenstein. The \ref{childrens_game|puzzles|reference} that Wittgenstein offers us (along the way to trying to dissolve the presuppositions that make it puzzling) center around the normative significance of beliefs/desires/intentions.}.
    \end{itemize}
    \item Both sides treat $D$ as true, but Team $O$ furthermore believes $O$ is true and that the order of explanation is $O \implies D$. However, Team $D$ takes $D$ as essential and needs not make any claim about ontology.

    \item Downstream of this are many of Kant's innovations. \begin{itemize}
    \item The minimum unit of awareness/experience is the judgment \begin{itemize}
    \item this comes from taking $D$ to be fundmental: it is the smallest thing we can be held responsible for
    \item Everything else (particular concepts like \emph{Fido the dog}, universal concepts like \emph{triangularity}, logical concepts) has to be understood in terms of the function it plays with respect to judgment.
    \end{itemize}
    \item The \emph{subjective} form of judgment (the ``I think..." that can accompany all judgments)
    \begin{itemize}
    \item Because it can accompany all representations, this is the emptiest form of judgment.
    \item The mark of "who is responsible for the judgment".
    \item To say ``\emph{I think} it is raining now.'' is to emphasize that \emph{I} am responsible (e.g. subject to criticism if you go outside and don't get wet).

    \end{itemize}
    \item The \emph{objective} form of judgment (the ``$x$ is ...'' or ``$x$ = ...'' for some object $x$). \begin{itemize}
    \item Mark of what you've made yourself responsible to.
    \item When saying ``That stone is 50 pounds.'', the stone has a certain authority over me (one looks to the stone to see whether I am right or wrong; it sets the standards of correctness). See the \ref{shopping|shopping list scenario|referenced}.
    \end{itemize}
    \end{itemize}
    \end{itemize}
