I wander in from a different culture, into an auction house, where the significance of waving your hand is bidding the next amount on whatever is being auctioned. All I know of the local customs is that waving usually is a greeting for people. So I go in there and greet my friend by waving. I'm unaware that, in this context, doing that has the significance of bidding \$500 for that armoire. Now, if, as a matter of fact, I'm held responsible there (``You've implicitly accepted these rules by going into the auction house!"), then I've actually bid. That's what I've done. Even though I didn't intend to do that, I didn't mean to do that. But I produced a performance that has that significance.

A parallel story: in Napoleon era, England, they needed sailors, which was a terrible life. But the law was that one had to voluntarily join Her Majesty's Navy. Because people were illiterate, taking the Queen's shilling from a duly authorized representative of Her Majesty's Government showed that you had voluntarily joined the service: if you did that, you \emph{had} joined the Navy. You had committed yourself. And so they'd go to the bars and wait until somebody was drunk and out of money to say ``Like a shilling for another drink, mate?" They weren't wearing the uniform or anything that shows that they were the duly authorized representatives, but they had the papers to show they were. You couldn't deny there were all these witnesses that you took the shilling from this person. That's an equivalent of having bid on the armoire: the law was, if you performed that act, regardless of intention, that counted as committing yourself.